Demography and selection since maize domestication

### 2015-06-05 manuscript.tex
update

\begin{figure}[b]
%\vspace*{.05in}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_unNeutralized}
\caption{Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize. \jri{needs larger legend/axis labels. x axis needs to say cM}}
\label{hardSweeps}
\end{figure}

>>>>

\begin{figure*}[b]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_unNeutralized_June} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_unNeutralized_June}
\caption{Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize and teosinte. A: Maize diversity; B: Teosinte
diversity.}
\label{hardSweeps}
\end{figure*}
